---
title: "Bayesian Analyse"
author: "XW"
date: "2022-11-03"
output: html_document
---

# Cheapter 3
## Figure 3.1
Todo: Toss a coin N times and compute the running proportion of heads

<span style="color: red;">Calculation of the probability of the coin toss</span>

set.seed function: generating the random number  
sample function: x the range of value, prob: probability of x  
cumsum function: cumulative Sums

```{r}
N <- 5000;
set.seed(.4740)
flipsequence = sample(x = c(0,1), prob = c(0.5,0.5), size = N,replace = TRUE)
r = cumsum( flipsequence )
n = 1:N
runprop = r/n
```

<span style="color: red;">Plot the cumulative probability</span>

type: "l","s","p","o","b","h"  
log: "x","y","xy"/"yx"  
xlab, ylab, main  
cex.axis,cex.lab,cex.main: margnification
col.axis,col.lab,col.main: color

lines function: lty (0=blank, 1=solid (default), 2=dashed, 3=dotted, 4=dotdash, 5=longdash, 6=twodash)  
more: help(par)

```{r}
plot(n, runprop, type="p", log = "x",
     xlim = c(1,N), ylim = c(0.0,1.0), cex.axis = 1,
     xlab = "Flip Number", ylab = "Proportion of Heads", cex.lab=1,
     main = "Running Proportion of Heads", cex.main = 1)
lines(c(1,N),c(.5,.5),lty = 5)
flipletters = paste(c("T","H")[flipsequence[1:10]+1],collapse="")
displaystring = paste("Flip Sequence = ", flipletters, "...",sep="")
text (5,.9,displaystring,adj=c(0,1),cex=1.3)
text(N, .3, paste("End Proportion = ", runprop[N]),adj=c(1,0),cex=1.3)
```
##Figure 3.3
TODO: Graph of normal probability density function, with comb of intervals

<span style="color: red;">Calculation of the variables</span>

seq function: generate a sequences, from .. to .., by.. / end with ..  
seq(from, to, by=which, length.out=nummber)
```{r}
meanval = 0;
sdval = 0.2;
xlow = meanval - sdval*3;
xhigh = meanval + sdval*3;
dx= 0.02;                                     # Interval width on x-axis
x = seq(from = xlow, to = xhigh, by = dx);    # Comb points along the x axis
y = (1/(sdval*sqrt(2*pi)))* exp (-.5 * ((x-meanval)/sdval)^2)
```

<span style="color: red;">Generate the Graph</span>

```{r}
plot(x, y, type="h", lwd=1, cex.axis=1.5,
     xlab = "x", ylab = "p(x)", cex.lab=1.5,
     main = "Normal Probability Density", cex.main=1.5)
lines(x,y)
area = sum(dx*y)
text(-sdval, .9*max(y), bquote(paste(mu, "=",.(meanval))), adj = c(1,.5))
text(-sdval, .8*max(y), bquote(paste(sigma, "=",.(sdval))), adj = c(1,.5))
text(sdval, .9*max(y), bquote(paste(Delta, "x = ",.(dx))), adj = c(0,.5))
text(sdval, .8*max(y), bquote(paste(sum(,x,), " ", Delta, "x p(x) = ",.(signif(area,3)))),
     adj = c(0,.5))
```
